The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-11-14 paper/ms.tex
minor changes

This paper is paper is structured as follows. In \S
\ref{sec:implementation} we present the implementation of bulk
rotation into the Monte Carlo codes, paying special attention to coordinate
definitions. We also list the different physical parameters in
the simulated grid of models. In the next \S \ref{sec:results} we present the
results of the simulations, with special detail to quantities in the
line that show a clear evolution as a function of the sphere
rotational velocity. In \S \ref{sec:discussion} we discuss the
implications of our results in the interpretation of LAEs
observations and further refinements that can be implemented in the
theoretical modelling of the \ly line. In the last section we present
our conclusions.

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesCentral.png}
  \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesHOM.png}
\end{center}
\caption{Shape of the \ly line for
    different velocities rotational velocities for spherical
    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows
    the central (homogeneous) photon distribution. All photons were
    taken into  account regardless of their final direction of propagation.
    \label{fig:differentvelocities}}  
\end{figure*}

@@

\begin{figure}
  \includegraphics[scale=0.35]{OF_spheres.png}
  \caption{The two solid circles show the two different spherical
    off-centred emitting  regions. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction and the observer is
    along the $\hat{\j}$ direction (where the reader is). 
    \label{fig:OCspheres}} 
\end{figure}

The model with homogeneous radiation sources allows to study the
effect of radiation sources distributed with a different symmetry than
the gas. We select photons emitted in off-centred spheres 
with respect to the gas distribution.

@@

We study first the angular deviations of the outgoing photons with respect
to an isotropic flux. We follow \cite{Zheng2013} to estimate the flux
as a function of the angle $\Theta$ formed by the outgoing photons and
a fixed direction (the $\vec{k}$ direction in this case). This is
expressed by

\begin{equation}
F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
\end{equation}
%
where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
$\Delta N$ is the number of photons in a angular bin $\Delta
\Theta$. This definition satisfies the condition
$\int_{-1}^{1}F(\mu)d\mu/2=1$.

In the the off-center emission the variations  in the $\mu$ distribution
$\mu$ increase with the rotational velocity. For $V_{\rm max}= 50$\kms
 $\Delta \mu \leq 7\%$; $V_{\rm max}=100$\kms, $\Delta \mu\leq 12\%$
and $V_{\rm max}=200$\kms, $\Delta\mu\leq 15\%$ (NOTE: regardless of
$\tau$??). This implies a strong dependence of the observed flux on
the relative position of an observer.  In contrast,the central and
homogeneous source distributions only show a weak anisotropy at the level of
$\Delta\mu\leq 3\%$.

Figure \ref{fig:OC_profiles} show the spectra for the two off-centered
spheres located at $C=\pm0.5R$.  The most interesting effect is that
emission is that in  some models ($\tau = 10^6, V=100,200$\kms and $\tau =
10^7, V=200,300$\kms) the line presents three peaks (blue-shifted,
centred, red-shifted). However, we do not find any asymmetry in the line 
produced by the off-center emission. As in the homogeneous / central
model the line gets broader as the rotational velocity increases.

The results for the off-centered spheres placed closed to the center
at $C=\pm 0.25R$ do not display the features discussed above for the
spheres at $C=\pm0.5R$.

\begin{figure}
\includegraphics[scale=0.35]{mu_OC.png} \caption{Flux angular 
  dependency for off-center distribution. Different line widths
  illustrate different rotational velocities.\label{fig:OCflux}} 
\end{figure}

\begin{figure*}
\includegraphics[scale=0.3]{OC_profiles.png}
\caption{\ly profiles for the off-center positions. Dashed/solide
  lines represents spheres centered at $-0,5R/+0.5R$.
   \label{fig:OC_profiles}} 
\end{figure*}

>>>>

This paper is structured as follows. In \S
\ref{sec:implementation} we present the implementation of bulk
rotation into the Monte Carlo codes, paying special attention to coordinate
definitions. We also list the different physical parameters in
the simulated grid of models. In the next \S \ref{sec:results} we present the
results of the simulations, with special detail to quantities in the
line that show a clear evolution as a function of the sphere
rotational velocity. In \S \ref{sec:discussion} we discuss the
implications of our results in the interpretation of LAEs
observations and further refinements that can be implemented in the
theoretical modelling of the \ly line. In the last section we present
our conclusions.

@@

\begin{figure*}
  \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesCentral.png}
  \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesHOM.png}
\caption{Shape of the \ly line for
    different velocities rotational velocities for spherical
    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows
    the central (homogeneous) photon distribution. All photons were
    taken into  account regardless of their final direction of propagation.
    \label{fig:differentvelocities}}  
\end{figure*}

@@

\begin{figure}
  \includegraphics[scale=0.3]{OF_spheres.png}
  \caption{The two solid circles show the two different spherical off-centred emitting
    regions. The angular velocity vector is defined to be along the
    $\hat{\i}$ direction and the observer is along the $\hat{\j}$ direction (where
    the reader is). 
    \label{fig:OCspheres}} 
\end{figure}

The model with homogeneous radiation sources allows to study the
effect of radiation sources distributed with a different symmetry than
the gas. We select photons emitted in spheres that are off-centred
with respect to the gas distribution.

@@

We study first the deviations of the received flux on the surface of the
sphere. We follow \cite{Zheng2013} to estimate the flux seen by an
observer located at an angle $\Theta$ (distant observer angle)
normalized to the isotropic flux:

\begin{equation}
F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
\end{equation}
%
Where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
$\Delta N$ is the number of photons in a angular bin $\Delta
\Theta$. This definition satisfies the condition
$\int_{-1}^{1}F(\mu)d\mu/2=1$.

For the central and homogeneous source distributions we find that the
level of isotropy angular dependency represented by $\mu$ doesn't show
a considerable variation in particular the observer would infer
luminosities  different from the isotropical value only at levels $<
3\%$. This values were obtained for a run with $V_{\rm max}=(50kms^{-1}, 
100kms^{-1}, 200kms^{-1}, 300kms^{-1})$ and $\tau_{\rm H}=10^{5}, 10^{6}, 
10^{7}$ and $N_{\gamma}=10^{5}$ photons.

For the Off-center emission Fig.\ref{fig:OCflux} the variations of 
$\mu$ increase as the rotational velocity increase, for $V_{\rm max}=(50kms^{-1}$
 $\bigtriangleup\mu \leq 7\%$ , for $V_{\rm max}=(100kms^{-1}$
$\bigtriangleup\mu\leq 12\%$ and finally for $V_{\rm max}=(200kms^{-1}$
$\bigtriangleup\mu\leq 15\%$. This would imply that the amount of flux
we measure would depend in the angle between our line of sight and 
the rotation axis of the galaxy. 
%%%%%%%

The outgoing spectra for two different spheres located at $\pm 0.5R$ 
are shown in Fig.\ref{fig:OC_profiles}, we have shown this positions because
the resulting profiles show new interesting morphologies than are not
found in the $\pm 0.25R$ case.

\begin{figure}
\includegraphics[scale=0.3]{mu_OC.png}
\caption{Flux angular dependency for Off-center distribution, different line widths illustrate different
off-center positions.
   \label{fig:OCflux}} 
\end{figure}

The main effect we found in the off-center emission is that for 
some models ($\tau = 10^6, V=100 km s^{-1}$ and $\tau = 10^7, V=200 km s^{-1}$)
the line presents three peaks (blue-shifted, centred, red-shifted),
to obtain clearest profiles concerning this results we run three models 
with $\tau_{\gamma}=10^{6}$, This profiles are shown in 
Fig.\ref{fig:OC_profiles_N6}, where we clearly observe the presence of 
three peaks, and also we do not find any asymmetry in the line 
produced by the off-center emission.

For models with ($[\tau = 10^{5}, V=100 km s^{-1}]$ ,
$[\tau = 10^6, V=200 km s^{-1}]$ and $ [\tau = 10^{7}, 
V=300 km s^{-1}]$) the centred line is dominant but the presence of
the redder and bluer peak in also present which is also a new result.
Also as in the homogeneous / central model the line is broader at high 
rotational velocities.

\begin{figure*}
\includegraphics[scale=0.3]{OC_profiles.png}
\caption{$\mathrm{Ly}\alpha$ profiles for the off-center positions.
dashed lines represents spheres locate at $-0,5R$ while solid lines 
represents spheres at $0.5R$)
   \label{fig:OC_profiles}} 
\end{figure*}

\begin{figure*}
\includegraphics[scale=0.3]{NewPanel_N6_atpm5.png}
\caption{$\mathrm{Ly}\alpha$ profiles for the off-center positions.
green lines represents spheres locate at $-0,5R$ while red lines 
represents spheres at $0.5R$)
   \label{fig:OC_profiles_N6}} 
\end{figure*}
